%-------------------------
% Resume-Latex
% Author : MorganKryze
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\input{config.tex}

\begin{document}

%----------HEADING--------------
\begin{center}
  \textbf{\Huge Jorge Benavides Macías} \\ \vspace{1pt}
  \href{mailto:bmacias.jorge@gmail.com}{\underline{bmacias.jorge@gmail.com}} $|$ 
  \href{https://www.linkedin.com/in/jorgebenavidesm/}{\underline{LinkedIn}} $|$
  \href{https://www.github.com/rhyloo}{\underline{Github}} $|$
  \href{https://www.rhyloo.com}{\underline{Personal Website}} $|$ 
  (+34) 611805599 \\
  \vspace{6pt}
  \textbf{\small{Junior Embedded Engineer passionate about contributing to full embedded development design. Skilled in microcontroller programming (ARM, STM32, ESP32), PCB design (Altium/Eagle), and IoT prototyping. Eager to grow within collaborative teams on projects spanning hardware/software co-design, testing, and deployment.}}
\end{center}
%-------------------------------

%-----------EXPERIENCE----------
\section{Work Experience}
\resumeSubHeadingListStart
\resumeSubheading{\textbf{Junior Cybersecurity \& Microelectronics Engineer}}{Jul. 2024 -- Present}
                 {InnovaIRV}{Malaga, Spain}
                 \resumeItemListStart
                 \resumeItem{Led cybersecurity needs assessments for over 15 Andalusian technology companies through executive/CISO interviews, identifying critical gaps in network security, access control and incident response.}
                 \resumeItem{Authored 150-page technical report with prioritized countermeasures as regional cybersecurity roadmap to Andalusia’s Goverment.}
                 \resumeItem{Technical execution of a full project lifecycle (€600k budget) for \textit{Impulso\&Crece2024} digitalization initiative funded by regional authorities.}
                 \resumeItemListEnd

                 \resumeSubheading{\textbf{R\&D Jr. Electronic Engineer}}{Mar. 2024 -- Jul. 2024} % <- Fechas abreviadas
                                  {Quandum AeroSpace S.L.}{Malaga, Spain} % <- Tilde añadida
                                  \resumeItemListStart % <- Faltaba este
                                  
                                  \resumeItem{Designed a 15W wireless charging system for vertical wind turbines using Altium, reducing component count by 30\%.}
                                  \resumeItem{Implemented RTOS-based motor control on ESP32.}
                                  \resumeItem{Collaborated on mechanical design (CATIA), PLC automation, and Linux-based version control system administration.} % <- Más conciso
                                  \resumeItemListEnd

                                  \resumeSubheading{\textbf{Jr. Electronic Engineer}}{Sept. 2023 -- Mar. 2024}
                                                   {DHV Technology}{Malaga, Spain}
                                                   \resumeItemListStart
                                                   \resumeItem{Designed solar panels for space applications using SolidWorks (3D modeling) and Altium (PCB design).} % <- Sin "I"
                                                   \resumeItemListEnd
                                                   \resumeSubHeadingListEnd
                                                   %-----------------------------
                                                   \vspace*{-10pt}
                                                   %-----------PROJECTS----------
                                                   \section{Projects}
                                                   \resumeSubHeadingListStart
                                                   \resumeProjectHeading{
                                                     \href{https://www.rhyloo.com/projects/TFG.html}{\textbf{PCB Design for Robotic Gripper}} $|$ \emph{C, ARM, PSoC, LabView, Eagle} $|$ \small{\href{https://doi.org/10.1007/978-3-031-59167-9_34}{DOI}}}{}
                                                   \resumeItemListStart
                                                   \resumeItem{Designed and manufacturing a PCB for data acquisition from resistive tactile sensors integrated into a robotic manipulator's gripper. This involved full process design, including component selection, material procurement, and PCB trace routing, it incorporated a PSoC in a QFN package.}
                                                   \resumeItem{Developed a master-slave architecture in C for ARM, collecting data from multiple sensors via SPI and UART communication, with debugging facilitated by LabView.}
                                                   \resumeItemListEnd
                                                   \resumeProjectHeading
                                                       {\href{https://www.rhyloo.com/projects/LaCaja.html}{\textbf{LaCaja}} $|$ \emph{C, MQTT, MongoDB, JavaScript, HTML, CSS, NodeRED} $|$ \small{\href{https://www.elespanol.com/malaga/economia/tecnologia/20230410/siga-instrucciones-chiquito-calzada-contratado-google-malaga/754174577_0.html}{News} - \href{https://sites.google.com/view/lacaja-malaga/inicio}{Web} - \href{https://github.com/izanamador/infind}{Repository}}}{}
                                                       \resumeItemListStart
                                                       \resumeItem{Earned the opportunity to visit Google's Malaga offices and present the project.}
                                                       \resumeItem{Crafted an AI-driven escape room experience featuring "Chiquito de la Calzada", offering participants a chance to win a position at Google.}
                                                       \resumeItem{Designed 2/5 games (software \& hardware), managing PCB soldering and sensor connections.} % <- Typo corregido + detalle
                                                       \resumeItemListEnd
                                                       \resumeProjectHeading
                                                           {\href{https://www.rhyloo.com/projects/VHDL.html}{\textbf{Digital Design}} $|$ \emph{VHDL, git } $|$ \small{\href{https://github.com/rhyloo/VHDL_at_University}{Repository}}}{}
                                                           \resumeItemListStart
                                                           \resumeItem{Proficient in designing, simulating, and synthesising digital circuits using VHDL.}
                                                           \resumeItem{Developed diverse testbenches, from debouncers to factorial calculation systems, and integrated MicroBlaze IP core into a Mastermind-like game.}
                                                           \resumeItemListEnd
                                                           \resumeSubHeadingListEnd
                                                           %-----------------------------

                                                           %-----------EDUCATION-----------
                                                           \section{Education}
                                                           \resumeSubHeadingListStart
                                                           \resumeSubheading
                                                               {\href{}{\textbf{University of Malaga}}}{Malaga, Spain}
                                                               {Master's Degree in electronic systems for smart environments}{Sep. 2024 -- Present}
                                                               \resumeSubheading
                                                                   {\href{}{\textbf{University of Malaga}}}{Malaga, Spain}
                                                                   {{Bachelor in electronics, robotics \& mechatronics. Major in robotics \& automation}}{Sept. 2018 -- Sept. 2023}
                                                                   \resumeSubHeadingListEnd
                                                                   %-------------------------------
                                                                   
                                                                   %-----PROGRAMMING SKILLS------
                                                                   \section{Technical Skills}
                                                                   \begin{itemize}[leftmargin=0.15in, label={}]
                                                                     \small{\item{
                                                                         \textbf{Languages}{: Spanish (native), English proficient (B1)} \\
                                                                         \textbf{Embedded Systems}{: STM32, ESP32, AVR, RTOS, PCB Design (Altium/Eagle/KiCAD) and 3D CAD Model (CATIA, SolidWorks)} \\
                                                                         \textbf{Programming}{: C/C++, Python, Bash, VHDL} \\
                                                                         \textbf{Tools}{: Git, Docker, Vivado, LabVIEW, MATLAB, Emacs} % <- LabVIEW corregido
                                                                     }}
                                                                   \end{itemize}
                                                                   %-----------------------------
\end{document}
