%-----------EXPERIENCE----------
\section{Work Experience}

\begin{workexp}

  \job{System Embedded Engineer}{Sept. 2025 -- Present}{Clue Technologies}{Malaga, Spain}{
    \item Drive systems validation and hardware stress testing for general-purpose mission computers in avionics and defense.
    \item Developed customized C and Python stress-testing software to validate aerospace communication protocols, including RS485, RS422, ARINC 818, Ethernet and fiber optics.
    \item Engineered video processing benchmarks and hardware stress tools to evaluate maximum thermal limits, power consumption, and peak system reliability.
    \item Validated low-level software stacks including Bare-metal applications, VxWorks RTOS environments, and U-Boot bootloaders.
  }

  \job{Junior Cybersecurity \& Microelectronics Engineer}{Jul. 2024 -- Sept. 2025}{InnovaIRV}{Malaga, Spain}{
    \item Led cybersecurity needs assessments for over 15 Andalusian technology companies through executive/CISO interviews, identifying critical gaps in network security, access control, and incident response.
    \item Authored a 150-page technical report with prioritized countermeasures as a regional cybersecurity roadmap for Andalusia's Government.
    \item Technical execution of a full project lifecycle (€600k budget) for \textit{Impulso\&Crece2024} digitalization initiative funded by regional authorities.
  }

  \job{R\&D Jr. Electronic Engineer}{Mar. 2024 -- Jul. 2024}{Quandum AeroSpace S.L.}{Malaga, Spain}{
    \item Designed a 15W wireless charging system for vertical wind turbines using Altium, reducing component count by 30\% and optimizing overall PCB layout size.
    \item Implemented RTOS-based motor control on ESP32.
    \item Collaborated on mechanical design (CATIA), PLC automation, and Linux-based version control system administration.
  }

  %% \job{Jr. Electronic Engineer}{Sept. 2023 -- Mar. 2024}{DHV Technology}{Malaga, Spain}{
  %%   \item Managed electronic and mechanical design tasks for 7 space-sector projects concurrently, covering SmallSats, CubeSats, and custom solar panels under strict ECSS standards.
  %%   \item Executed end-to-end component engineering tasks, including BOM management, component selection, derating analyses, power consumption budgeting, and magnetic moment calculations.
  %%   \item Performed 3D mechanical routing for solar cell wiring harnesses using SolidWorks and developed rigid-flex PCB designs using Altium.
  %%   \item Generated qualification test plans, analyzed environmental test results, and authored comprehensive technical reports for international aerospace clients.
  %% }

\end{workexp}
