%-----------PROJECTS----------
\section{Projects}

\begin{projlist}

  \proj{
    \href{https://www.rhyloo.com/projects/TFG.html}{\textbf{PCB Design for Robotic Gripper}}
    $|$ \emph{C, ARM, PSoC, LabView, Eagle}
    $|$ \small{\href{https://doi.org/10.1007/978-3-031-59167-9_34}{DOI}}
  }{
    \item Designed and manufacturing a PCB for data acquisition from resistive tactile sensors integrated into a robotic manipulator's gripper. This involved full process design, including component selection, material procurement, and PCB trace routing, it incorporated a PSoC in a QFN package.
    \item Developed a master-slave architecture in C for ARM, collecting data from multiple sensors via SPI and UART communication, with debugging facilitated by LabView.
  }

  \proj{
    \href{https://www.rhyloo.com/projects/LaCaja.html}{\textbf{LaCaja}}
    $|$ \emph{C, MQTT, MongoDB, JavaScript, HTML, CSS, NodeRED}
    $|$ \small{
      \href{https://www.elespanol.com/malaga/economia/tecnologia/20230410/siga-instrucciones-chiquito-calzada-contratado-google-malaga/754174577_0.html}{News}
      -- \href{https://sites.google.com/view/lacaja-malaga/inicio}{Web}
      -- \href{https://github.com/izanamador/infind}{Repository}
    }
  }{
    \item Earned the opportunity to visit Google's Malaga offices and present the project.
    \item Crafted an AI-driven escape room experience featuring ``Chiquito de la Calzada'', offering participants a chance to win a position at Google.
    \item Designed 2/5 games (software \& hardware), managing PCB soldering and sensor connections.
  }

  \proj{
    \href{https://www.rhyloo.com/projects/VHDL.html}{\textbf{Digital Design}}
    $|$ \emph{VHDL, git}
    $|$ \small{\href{https://github.com/rhyloo/VHDL_at_University}{Repository}}
  }{
    \item Proficient in designing, simulating, and synthesising digital circuits using VHDL.
    \item Developed diverse testbenches, from debouncers to factorial calculation systems, and integrated MicroBlaze IP core into a Mastermind-like game.
  }

\end{projlist}
